---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SteamGamesReviewFilter

<!-- badges: start -->

<!-- badges: end -->

The goal of SteamGamesReviewFilter is to split a column of review data derived from the `steam_games` data set into three pieces of data via delimiters. These pieces are:

\- `_rating`: Overall rating of game. String. Ex: Positive, Negative, Mixed.

\- `_reviews`: Number of reviews game received. Numeric. Ex: 183, 18, 67392.

\- `percent_positive_`: % of reviews that are positive. Numeric. Ex: 98, 12, 3.

It is expected that the review data is formatted with specific delimiters present in the `steam_games` data.

## Installation

You can install the development version of SteamGamesReviewFilter from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("stat545ubc-2025/assignment-b2-Jessica-Sun")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(SteamGamesReviewFilter)
library(datateachr)
library(tidyverse)
library(stringr)
library(forcats)

split_steam_reviews(steam_games, "recent")
split_steam_reviews(steam_games, "all")
```
